Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-09-04 paper.tex
Add references to Deaton thesis and Foucart MC-M1 paper

For merger simulations \cite{fouc2016-m1_evolve_n} have recently
expanded their M1 transport code
to also evolve the zeroth-angular moment of the number density,
providing total energy densities and average energies throughout the
simulated volume.
Even so, with M1 transport codes only evolving two angular moments
and one or two energy moments,
they can extract only limited angular and spectral information
from the neutrino fields.

@@

%\subsubsection*{Why ray tracing?}
In this work we present a ray tracing method to compute neutrino distribution
functions from state-of-the-art general relativistic M1 transport
hydrodynamics simulations.
We choose ray tracing because it is conceptually simple,
numerically inexpensive,
and extends to high resolution in energy and angle
by simply increasing the number of rays sampled.
Furthermore, the computational implementation parallellizes trivially.

@@

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Unfinished.
Optically thick star in Schwarszchild.
Total luminosity at infinite separation may be computed by
computing the radial energy flux at a finite separation from the star, $r$,
and using $p_t$ for the energy. We compute this asymptotic luminosity
at several radii, $r$, and show that the luminosity is independent of
the observer's radius.
\footnote{TODO: compute $L$, put in figure}
Also compare a few geodesics in Kerr to analytic.

>>>>

For merger simulations, \cite{fouc2016-m1_evolve_n} have recently
expanded their M1 transport code
to also evolve the zeroth-angular moment of the number density,
providing total energy densities and average energies throughout the
simulated volume.
Even so, with M1 transport codes only evolving two angular moments
and one or two energy moments,
they can extract only limited angular and spectral information
from the neutrino fields.

@@

%\subsubsection*{Why ray tracing?}
Angular and spectral neutrino distributions in neutron star merger simulations may
be available soon, for example with the coupled Monte-Carlo-M1 scheme presented in
\citep{fouc2017-m1_with_mc}.
In this work, however, we present a ray tracing method to compute neutrino
distribution functions from the existing state-of-the-art general relativistic M1
transport hydrodynamics simulations.
We choose ray tracing because it is conceptually simple,
numerically inexpensive,
and extends to high resolution in energy and angle
by simply increasing the number of rays sampled.
Furthermore, the computational implementation parallellizes trivially.

@@

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Unfinished: describe and point readers to Asano-Fukuyama test presented
in thesis ~\cite{deat2015-thesis}.
Also compare a few geodesics in Kerr to analytic.
\footnote{TODO: compute some geodesics in Kerr}
